\documentclass[a4paper]{article}

\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage{avant}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\textheight=10in
\pagestyle{empty}
\raggedright

\renewcommand{\familydefault}{\sfdefault}
\usepackage[left=1in,right=1in,bottom=1in,top=1in]{geometry}

\newcommand{\bull}{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{\textbf{#1}}}  % Added bold and section spacing
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}

% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\vspace*{-20mm}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{{\LARGE Ali Mashally}}
   & Email: \href{mailto:}{alimuhammadali@proton.me}\\
  \href{https://github.com/blackaly}{Github: ~~github.com/blackaly} & \href{tel:+201093826899}{EG Number: +201093826899} \\
  \href{https://codeforces.com/profile/i_alimuhammad}{CodeForces: ~codeforces.com/profile/i\_alimuhammad} \\
\href{https://www.hackerrank.com/alimashally?hr_r=1}{HackerRank: ~https://www.hackerrank.com/alimashally} \\
\href{https://ctflearn.com/user/_ajin}{CTFLearn: ~https://ctflearn.com/user/\_ajin} \\
  \href{https://www.linkedin.com/in/ali-mashally/}{LinkedIn: ~https://www.linkedin.com/in/ali-mashally/} \\

\end{tabular*}

\header{Introduction}
I am a dedicated Software Engineer with a strong foundation in computer science fundamentals, specializing in back-end development while also possessing a solid grasp of front-end technologies. My passion for problem-solving and continuous learning drives me to create efficient and innovative solutions. With the successful completion of my military service, I bring a strong work ethic, discipline, and a commitment to excellence to every project.

\header{Education}

\textbf{Modern Academy} \hfill Cairo, Maadi
\\
Bachelor of Computer Science \hfill Graduated in 2023 with \textbf{very good} grade \\


\header{Experience}

\textbf{Project-Egy} \hfill Remote \& On Site
\\
\textit{Software Engineer (Full-time internship)} \hfill May 2022 - Jul 2022
\begin{itemize} \itemsep -2pt 
    \item Reviewed business requirements to design scalable solutions.
    \item Collaborated as a back-end developer and agile team member to build integrations with various platforms.
    \item Developed and maintained RESTful APIs used by front-end engineers.
    \item Implemented automation solutions for enterprises and e-commerces.
    \item Optimized Sanai3yTrend's response time from 14 seconds to 1 second by applying appropriate data structures, algorithms, and Entity Framework best practices.
    \item Worked on four E-Commerce projects (MedLife, Salamtak, Sanai3yTrend, Wasta)
\end{itemize}
\textbf{DFC} \hfill Remote \& On Site
\\
\textit{Software Engineer (Part-time)} \hfill Jan 2024 - NOW
\begin{itemize} \itemsep -2pt 
    \item Developed and implemented automation scripts using Python to streamline business processes, reducing manual effort by 35\% and improving operational efficiency.
    \item Prepared and submitted technical proposals for industry conferences (e.g., Techne), highlighting innovative automation solutions and their business impact.
    \item Networked with industry experts at conferences to stay updated on emerging technologies and bring new ideas back to the organization.
\end{itemize}


\header{Skills Summary}
\vspace*{2mm}
\begin{tabular}{ll}
    Programming Languages: & C\#, C/C++, PHP (prior experience), Python \\
    Frameworks: & .NET(aka. Core), ASP .NET MVC, ASP .NET WebApi, Angular\\
    Databases: & MySQL, SQLite, SQL Server \\
    Unix-System: & Bash-Scripting, Linux System Programming, Docker \\
    Web: & RESTful WebServices, Swagger/OpenAPI, Google Cloud Platform (GCP) \\
    Other: & Git, SSH with Xvfb manipulation \\
\vspace*{2mm}
\end{tabular}

\header{Projects}
\textbf{CodeHex} {\sl C\#}
Designed and developed a responsive web application using Angular and Angular Material to streamline problem-solving competitions, enabling real-time judging, scoring. \href{https://github.com/blackaly/CodeHex}{ \sl \textbf{Github}}

\textbf{Soundit} {\sl C\#}
\\A C\# application that performs lexical analysis to convert a sequence of characters (string) into tokens, removes newlines and comments, and processes YouTube video URLs to extract audio stream URLs and video titles. \href{https://github.com/blackaly/soundit/}{ \sl \textbf{Github}}

\textbf{MOVIE API} {\sl ASP .NET CORE Web API, identity, Drapper}
\\Movie Library System. \href{https://github.com/blackaly/MovieAPI} {\sl \textbf{Github}}

\textbf{Classify} {\sl Python, OOP (Strategy pattern), BBC News Model, NLTK, sklearn, selenium}
\\Text Classification for News Articles by entering raw text input or the link of a supported website in the application. \href{https://github.com/blackaly/classify} {\sl \textbf{Github}}

\

\textbf{City Analysis} {\sl Python}
\\An analysis project that generates statistics on the most popular stations and trips, total and average trip duration, and bikeshare user demographics. (May 2020)

\textbf{Library system} {\sl C\#, WPF, CSV Helper}
\\A class library for managing authors' books data using CSV files with basic CRUD operations.

\textbf{University System (Desktop)} {\sl Java, SQL}
\\A desktop application connected with SQL Server, utilizing CRUD operations on a side server client, managing student and professor data, and calculating student GPAs. (May 2021)



\header{Activities}
\textbf{Modern Academy ECPC Community}
\vspace{-6pt} 
\begin{itemize} \itemsep -2pt
    \item Participated in the 2022 Egyptian Collegiate Programming Contest.
    \item Achieved 10th place in the 2022 MAM Collegiate Programming Contest. [\href{https://icpc.global/ICPCID/6VCK89VLPTH4}{Details}]
\end{itemize}

\textbf{icmtc}
\vspace{-6pt} 
\begin{itemize} \itemsep -2pt
    \item Participated in the 2023 The International Competition of the Military Technical College (CTF Contest).
    \item Secured 51st place out of 106 in the scoreboard. [\href{https://icmtc.egcert.eg/scoreboard}{Schizophrenia Team}]
\end{itemize}

\end{document}
